Final Project

### 2025-04-29 MSSC5750_Project.qmd

>>>>

Now doing a basic logistic regression with/without lasso selection
```{R}

# We need a train/test split. We will use 80/20
# can use uniform distribution, set seed for reproducability
set.seed(100)
forTrain<-runif(nrow(data))<.8

trainData<-data[forTrain,]
testData<-data[!forTrain,]

# First creating logistic regression with all our variables
logModel <- glm(loan_status ~ person_age + person_gender + person_education + person_income + person_emp_exp + person_home_ownership +loan_amnt + loan_intent + loan_int_rate + loan_percent_income + cb_person_cred_hist_length + credit_score + previous_loan_defaults_on_file, data=trainData, family= binomial )

# Repeating but removing the variables not relevant in lasso
# removed(person cred length, person_emp_exp person_income person_gender person_education person_age)
logModelLasso <- glm(loan_status ~ person_home_ownership +loan_amnt + loan_intent + loan_int_rate + loan_percent_income  + credit_score + previous_loan_defaults_on_file, data=trainData, family= binomial )

testData$logisticPred <- round(predict(logModel, testData, type='response'))
testData$logisticLassoPred <- round(predict(logModelLasso, testData, type='response'))

# Matrix for regular log
confusionMatrix(factor(testData$logisticPred), factor(testData$loan_status), positive = '1')

# Matrix for lasso log
confusionMatrix(factor(testData$logisticLassoPred), factor(testData$loan_status), positive = '1')
